---
title: "AS3-2: 股市動態"
author: "第 5 組"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

**股票動態**

股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 
```{r}
IBM = read.csv("data/IBMStock.csv")
GE = read.csv("data/GEStock.csv")
ProcterGamble = read.csv("data/ProcterGambleStock.csv")
CocaCola = read.csv("data/CocaColaStock.csv")
Boeing = read.csv("data/BoeingStock.csv")
#將每一個csv檔案個別命名並存入指定的資料框
```


分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：

+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>

###  Section-1 Summary Statistics

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
nrow(Boeing) #由於5個資料框的觀察值數量一樣，只取其一來計算列的數量，nrow = number of row 列的數量
```


__§ 1.2__ What is the earliest year in our datasets?
```{r}
IBM$Date = as.Date(IBM$Date, "%m/%d/%y") 
# as.Date 是把括弧內的資料框更改成特定的日期格式 %m （2位數呈現月）/%d （用2位數呈現日）/%y （用2位數呈現年）
GE$Date = as.Date(GE$Date, "%m/%d/%y") 

CocaCola$Date = as.Date(CocaCola$Date, "%m/%d/%y") 

ProcterGamble$Date = as.Date(ProcterGamble$Date, "%m/%d/%y") 

Boeing$Date = as.Date(Boeing$Date, "%m/%d/%y")

IBM$Date %>% min() %>% format(.,"%Y") # 使用min函數找出IBM中Date最小的年份並且用format函數求得指定格式 %Y （用4位數呈現年）列印出答案，而句點符號 . 管線符號%>%的前一項

```

__§ 1.3__ What is the latest year in our datasets?
```{r}
GE$Date %>% max %>% format(.,"%Y") # 找出GE中Date最大的年份並且指定用格式 %Y （用4位數呈現年）列印出答案
```

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
mean(IBM$StockPrice) #使用mean函數求得IBM公司股價的平均值
```

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
min(GE$StockPrice) #使用min函數求得GE公司股價的最小值
```

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
max(CocaCola$StockPrice) #使用max函數求得Cocacola公司股價的最大值
```

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
median(Boeing$StockPrice) #使用median函數求得Boeing公司股價的中位數
```

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
sd(ProcterGamble$StockPrice) #使用sd函數求得ProcterGamble公司股價的標準差
```

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period?
```{r}
plot(x = CocaCola$Date , y = CocaCola$StockPrice,type="l") #使用plot函數可以畫出 x和y軸的點狀圖，指定x軸和y軸後利用type=“l”讓點變成線l代表line的意思
CocaCola$StockPrice %>% which.max() %>% CocaCola$Date[.] %>% format(., "%Y") #which.max可以找出最大值的位置，然後再用索引中括號找出符合格式“%Y”的對應值列印出來，句點符號.代表管線符號%>%的前一項
CocaCola$StockPrice %>% which.min() %>% CocaCola$Date[.] %>% format(., "%Y") #which.min可以找出最小值的位置，然後再用索引中括號找出符合格式“%Y”的對應值列印出來，句點符號.代表管線符號%>%的前一項


# highest = 1973 lowest = 1980 
```


__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?
```{r}
plot(x = CocaCola$Date, 
     y = CocaCola$StockPrice, 
     type="l", col="red", ylim=c(0,210))#使用plot函數可以畫出 x和y軸的點狀圖，指定x軸和y軸後利用type=“l”讓點變成線l代表line的意思，plot函數中可以使用function col來指定顏色，ylim是指y軸的範圍要從0到210
lines(ProcterGamble$Date, 
      ProcterGamble$StockPrice, col="blue")#line函數可以在既有的plot圖加上另一條線，一樣可以使用function col來指定顏色以做出區別
lines(GE$Date, 
      GE$StockPrice, col="green")
lines(IBM$Date, 
      IBM$StockPrice, col="orange")
lines(Boeing$Date, 
      Boeing$StockPrice , col="purple")
legend("topright", pch=1, 
       col=c("red", "blue", "green", "orange", "purple"), 
       legend = c("Cocacola", "ProcterGamble", "GE", "IBM", "Beoing"))#legend函數可以在plot圖上指定的位置“topright”中標示出每個線對應的名字，pch=1是圖形1，可以參考（http://www.endmemo.com/program/R/pchsymbols.php） 來選取想要的圖形，這裡的特別注意的是col=c（）和legend=c（）括號裡面的顏色和名字順序要一致
abline(v=as.Date(c("2000-03-01")), lwd=1, col="grey") #abline函數可以在plot圖上面增加一條指定位置的線，v代表vertical垂直線，h代表horizontal水平線，lwd代表粗度，這邊也可以指定想要的顏色

#ProcterGamble 
```

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
plot(x = CocaCola$Date, 
     y = CocaCola$StockPrice, type="l", col="red")
lines(ProcterGamble$Date, 
      ProcterGamble$StockPrice, col="blue")
legend("topright", pch=1, 
       col=c("red", "blue"), 
       legend = c("Cocacola","ProcterGamble"))
abline(v=as.Date(c("1983-01-01")), lwd=1,col="grey") #同上
#  Cocacola going up while ProcterGamble going down 
```

(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
# Cocacola 
```


<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
index <- ( GE$Date >= as.Date("1995-01-01") ) & ( GE$Date <= as.Date("2005-12-31")  )#指定GE中Date的日期介於1995年1月1日及2005年12月31日之間的列數
GE[index,]  #再利用GE去索引這個區間找出是301到432列以方便後續plot畫圖的準確度 #[row,column] 

plot(CocaCola$Date[301:432], 
     CocaCola$StockPrice[301:432], 
     type="l", col="red", ylim=c(0,210), 
     xlab="Year",ylab="Companies Stock",  #xlab表示x軸的名稱，ylab為y軸的名稱，main則是標題的名稱
     main="Five companies stock line graph") 
lines(Boeing$Date[301:432], 
      Boeing$StockPrice[301:432], 
      type="l", col= "green", ylim=c(0,210))
lines(GE$Date[301:432], 
      GE$StockPrice[301:432], 
      type="l", col= "purple", ylim=c(0,210))
lines(IBM$Date[301:432], 
      IBM$StockPrice[301:432], 
      type="l", col= "blue", ylim=c(0,210))
lines(ProcterGamble$Date[301:432], 
      ProcterGamble$StockPrice[301:432], 
      type="l", col= "orange", ylim=c(0,210))
legend("topright", pch=1, 
       col=c("red", "green", "purple", "blue", "orange"), 
       legend = c("Cocacola", "Boeing", "GE", "IBM", "ProcterGamble"))
abline(v=as.Date(c("2000-03-01")), lwd=1,col="grey")  #同上



# GE 
```

__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}

# IBM 
```

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
index2 <- ( GE$Date >= as.Date("1997-01-01") ) & ( GE$Date <= as.Date("1997-12-31")  )
CocaCola[index2,]
plot(CocaCola$Date[325:336], 
     CocaCola$StockPrice[325:336], 
     type="l", col="red", ylim=c(0,210), 
     xlab="Year", ylab="Companies Stock", 
     main="Five companies stock line graph") 
lines(Boeing$Date[325:336], 
      Boeing$StockPrice[325:336], 
      type="l", col= "green", ylim=c(0,210))
lines(GE$Date[325:336], 
      GE$StockPrice[325:336], 
      type="l", col= "purple", ylim=c(0,210))
lines(IBM$Date[325:336], 
      IBM$StockPrice[325:336], 
      type="l", col= "blue", ylim=c(0,210))
lines(ProcterGamble$Date[325:336], 
      ProcterGamble$StockPrice[325:336], 
      type="l", col= "orange", ylim=c(0,210))
legend("topright", pch=1, 
       col=c("red", "green", "purple", "blue", "orange"), 
       legend = c("Cocacola", "Boeing", "GE", "IBM", "ProcterGamble"))
abline(v=as.Date(c("1997-09-01")), lwd=1,col="grey")
abline(v=as.Date(c("1997-11-01")), lwd=1,col="grey")  #同上

#ProcterGamble and Boeing 
```

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
index3 <- ( GE$Date >= as.Date("2004-01-01") ) & ( GE$Date <= as.Date("2005-12-31")  )
CocaCola[index3,]
plot(CocaCola$Date[409:432], 
     CocaCola$StockPrice[409:432], 
     type="l", col="red", ylim=c(0,210), 
     xlab="Year", ylab="Companies Stock", 
     main="Five companies stock line graph") 
lines(Boeing$Date[409:432], 
      Boeing$StockPrice[409:432], 
      type="l", col= "green", ylim=c(0,210))
lines(GE$Date[409:432], 
      GE$StockPrice[409:432], 
      type="l", col= "purple", ylim=c(0,210))
lines(IBM$Date[409:432], 
      IBM$StockPrice[409:432], 
      type="l", col= "blue", ylim=c(0,210))
lines(ProcterGamble$Date[409:432], 
      ProcterGamble$StockPrice[409:432], 
      type="l", col= "orange", ylim=c(0,210))
legend("topright", pch=1, 
       col=c("red", "green", "purple", "blue", "orange"), 
       legend = c("Cocacola", "Boeing", "GE", "IBM", "ProcterGamble")) #同上
#Boeing 
```


<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
mean(IBM$StockPrice) #先求出IBM公司股價的平均值
tapply(IBM$StockPrice , months(IBM$Date),mean) %>% sort #再使用tapply去找出每個月IBM公司股價的平均值後使用sort函數把他從小到大排列
#January, February, March, April, May 
```

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
tapply(GE$StockPrice, months(GE$Date),mean) %>% sort
tapply(CocaCola$StockPrice, months(CocaCola$Date),mean) %>% sort #同上
# April
```

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
tapply(GE$StockPrice, months(GE$Date), mean) #同上
# December 
```

<br><br><br>

