---
title: "AS3-3: 美國的人口統計和就業資料"
author: "第 5 組"
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

就業統計數據是政策制定者用來衡量經濟整體實力的最重要指標之一。在美國，政府使用現有人口調查（CPS）衡量失業率，該調查每月收集來自各種美國人的人口統計和就業信息。在本練習中，我們將使用講座中審查的主題以及一些使用2013年9月版的，具有全國代表性的數據集。數據集中的觀察結果代表2013年9月CPS中實際完成調查的人員，完整數據集有385個欄位，但在本練習中，我們將使用數據集CPSData.csv版本，它具有以下欄位：

+ `PeopleInHousehold`: 受訪者家庭中的人數。
+ `Region`: 受訪者居住的人口普查區域。
+ `State`: 受訪者居住的州。
+ `MetroAreaCode`: 都會區代碼，如受訪者不住都會區，則為NA；從代碼到都會區名稱的對應在`MetroAreaCodes.csv`中提供。
+ `Age`: 受訪者的年齡，以年為單位。 80代表80-84歲的人，85代表85歲及以上的人。
+ `Married`: 受訪者的婚姻狀況。
+ `Sex`: 受訪者的性別。
+ `Education`: 受訪者獲得的最高教育程度。
+ `Race`: 受訪者的種族。
+ `Hispanic`: 受訪者是否屬於西班牙裔。
+ `CountryOfBirthcode`: 識別受訪者出生國家的代碼。從代碼到國家名稱的映射在CountryCodes.csv文件中提供。
+ `Citizenship`: 受訪者的公民身份。
+ `EmploymentStatus`: 受訪者的就業狀況。
+ `Industry`: 受訪者的就業行業（僅在受僱的情況下可用）。

- - -

<br><br>

###  Section-1 Loading and Summarizing the Dataset

__§ 1.1__ How many interviewees are in the dataset?
```{r}
CPS = read.csv("data/CPSData.csv", stringsAsFactors=F)
nrow(CPS) 
#用nrow可看出CPS有多少筆記錄
```

__§ 1.2__ Among the interviewees with a value reported for the Industry variable, what is the most common industry of employment? Please enter the name exactly how you see it.
```{r}
table(CPS$Industry) [which.max(table(CPS$Industry))]
#用which.max可以看出在table(CPS$Industry)中最大值的位置
#再回到table(CPS$Industry)用[]去索引
```

__§ 1.3__ Which state has the fewest interviewees?
```{r}
table(CPS$State) [which.min(table(CPS$State))]
#先使用table()將CPS$Stae整理成一個表格
#再用which.min找出表格中的最小值的位置
#再回到table(CPS$State)用[]索引
```

Which state has the largest number of interviewees?
```{r}
table(CPS$State) [which.max(table(CPS$State))]
#先使用table()將CPS$Stae整理成一個表格
#再用which.max找出表格中的最大值的位置
#再回到table(CPS$State)用[]索引
```

__§ 1.4__ What proportion of interviewees are citizens of the United States?
```{r}
prop.table(table(CPS$Citizenship))[1]+prop.table(table(CPS$Citizenship))[2]
prop.table(table(!CPS$Citizenship=="Non-Citizen"))
#從CPS$Citizenship中去挑出非Non-Citizen的
#用table()整理成表格之後再用prop.table()去換算成比例
```

__§ 1.5__ For which races are there at least 250 interviewees in the CPS dataset of Hispanic ethnicity? (Select all that apply.) 

+ American Indian
+ Asian
+ cBlack
+ Multiracial
+ Pacific Islander
+ White

```{r}
table(CPS$Race, CPS$Hispanic)
#用table()去看Race與Hispanic之間的關係
#1代表是西班牙裔，0代表非西班牙裔
```
A:American Indian, Black, Multiracial, White

<br><br> 

- - -

###  Section-2 Evaluating Missing Values

__§ 2.1__ Which variables have at least one interviewee with a missing (NA) value? (Select all that apply.)

+ PeopleInHousehold
+ Region
+ State
+ MetroAreaCode
+ Age
+ Married
+ Sex
+ Education
+ Race
+ Hispanic
+ CountryOfBirthCode
+ Citizenship
+ EmploymentStatus
+ Industry

```{r}
summary(is.na(CPS))
#is.na()是邏輯向量，TRUE代表有NA
```
A:MetroAreaCode, Married, Education, EmploymentStatus, Industry

__§ 2.2__  Which is the most accurate:

+ The Married variable being missing is related to the Region value for the interviewee.
+ The Married variable being missing is related to the Sex value for the interviewee.
+ The Married variable being missing is related to the Age value for the interviewee. 
+ The Married variable being missing is related to the Citizenship value for the interviewee.
+ The Married variable being missing is not related to the Region, Sex, Age, or Citizenship value for the interviewee.

```{r}
table(CPS$Region, is.na(CPS$Married))
table(CPS$Sex, is.na(CPS$Married))
table(CPS$Age, is.na(CPS$Married))
table(CPS$Citizenship, is.na(CPS$Married))
#The Married variable being missing is related to the Age value for the interviewee.
```


__§ 2.3__ How many states had all interviewees living in a non-metropolitan area (aka they have a missing MetroAreaCode value)? For this question, treat the District of Columbia as a state (even though it is not technically a state).
```{r}
table(CPS$State , is.na(CPS$MetroAreaCode))
#TRUE= 表示有NA
#要找所有值都是NA(都是TRUE)
#找FALSE=0的都市
```
A:Alaska, Wyoming

How many states had all interviewees living in a metropolitan area? Again, treat the District of Columbia as a state.
```{r}
table(CPS$State , is.na(CPS$MetroAreaCode))
#同上
```
A:District of Columbia, New Jersey, Rhode Island

__§ 2.4__ Which region of the United States has the largest proportion of interviewees living in a non-metropolitan area?
```{r}
tapply(is.na(CPS$MetroAreaCode), CPS$Region, mean) %>% sort
#前面的is.na()是一串邏輯向量(TRUE=1,FALSE=0)
#上述tapply函數裡面使用mean，把is.na()去計算平均就可以得出比例
```
A:Midwest

__§ 2.5__ Which state has a proportion of interviewees living in a non-metropolitan area closest to 30%?
```{r}
tapply(is.na(CPS$MetroAreaCode), CPS$State, mean)%>% sort
#同上
```
A:Wisconsin

Which state has the largest proportion of non-metropolitan interviewees, ignoring states where all interviewees were non-metropolitan?
```{r}
#沿用上述表格
```
A:Montana

<br><br> 

- - -

###  Section-3 Integrating Metropolitan Area Data

__§ 3.1__ How many observations (codes for metropolitan areas) are there in MetroAreaMap?
```{r}
MetroAreaMap = read.csv("data/MetroAreaCodes.csv", stringsAsFactors = F)
nrow(MetroAreaMap)
#同1.1
```

How many observations (codes for countries) are there in CountryMap?
```{r}
CountryMap = read.csv("data/CountryCodes.csv", stringsAsFactors = F)
nrow(CountryMap)
#同1.1
```

__§ 3.2__ What is the name of the variable that was added to the data frame by the merge() operation?
```{r}
#merge()-兩個資料框的相加
CPS=merge(CPS, MetroAreaMap, by.x = "MetroAreaCode", by.y="Code", all.x = TRUE)
#CPS中的MetroAreaCode與MetroAreaMap的Code是一樣的
#all.x代表保留CPS的資料
```
A:MetroArea

How many interviewees have a missing value for the new metropolitan area variable?
```{r}
table(is.na(CPS$MetroArea))
#TRUE代表有NA的數量
```

__§ 3.3__ Which of the following metropolitan areas has the largest number of interviewees?
```{r}
which.max(table(CPS$MetroArea))
#先用table()整理CPS$MetroArea，再用which.max找出最大值
```

__§ 3.4__ Which metropolitan area has the highest proportion of interviewees of Hispanic ethnicity?
```{r}
tapply(CPS$Hispanic, CPS$MetroArea, mean)%>% sort %>% tail
#因為CPS$Hispanic是邏輯向量(TRUE=1，FALSE=0)，所以在tapply裡使用mean即可計算出比例
#再分別用sort與tail排出由小到大並找出最後的6個TOP6
```
A: Laredo, TX

__§ 3.5__ Determine the number of metropolitan areas in the United States from which at least 20% of interviewees are Asian.
```{r}
tapply(CPS$Race =="Asian" , CPS$MetroArea,mean) %>% sort(.,decreasing = T) %>% head
#同上
```
A: Honolulu, HI；San Francisco-Oakland-Fremont, CA；San Jose-Sunnyvale-Santa Clara, CA；Vallejo-Fairfield, CA

__§ 3.6__  Passing na.rm=TRUE to the tapply function, determine which metropolitan area has the smallest proportion of interviewees who have received no high school diploma.
```{r}
tapply(CPS$Education=="No high school diploma", CPS$MetroArea,mean, na.rm=TRUE) %>% sort %>% which.min
#同上
```


<br><br> 

- - -

###  Section-4 Integrating Country of Birth Data

__§ 4.1__ What is the name of the variable added to the CPS data frame by this merge operation?
```{r}
CPS=merge(CPS, CountryMap, by.x = "CountryOfBirthCode", by.y="Code", all.x = TRUE)
#同3.2
```
A:Country

How many interviewees have a missing value for the new metropolitan area variable?
```{r}
table(is.na(CPS$Country))
#同3.2
```
A:176

__§ 4.2__ Among all interviewees born outside of North America, which country was the most common place of birth?
```{r}
table(CPS$Country) %>% sort %>% tail
#用table()整理CPS$Country再用sort排序，再用tail找出後6個TOP6
```
A:Mexico

__§ 4.3__ What proportion of the interviewees from the "New York-Northern New Jersey-Long Island, NY-NJ-PA" metropolitan area have a country of birth that is not the United States? 
```{r}
tapply(CPS$Country!="United States",CPS$MetroArea=="New York-Northern New Jersey-Long Island, NY-NJ-PA", mean, na.rm=TRUE)
#同3.4
```
A:0.3087

__§ 4.4__ Which metropolitan area has the largest number (note -- not proportion) of interviewees with a country of birth in India? 
```{r}
head(sort(tapply(CPS$Country == "India", CPS$MetroArea, sum, na.rm=TRUE),decreasing = T))
#以MetroArea去做Counrty=India的加總，經過由小到大的排序之後再抓出後6個TOP6
```
A:New York-Northern New Jersey-Long Island, NY-NJ-PA

In Brazil?
```{r}
head(sort(tapply(CPS$Country == "Brazil", CPS$MetroArea, sum, na.rm=TRUE),decreasing = T))
#同上
```
A:Boston-Cambridge-Quincy, MA-NH

In Somalia?
```{r}
head(sort(tapply(CPS$Country == "Somalia", CPS$MetroArea, sum, na.rm=TRUE),decreasing = T))
#同上
```
A:Minneapolis-St Paul-Bloomington, MN-WI
<br><br><br>
